---
output:
  html_document: default
  pdf_document: default
---
#Title-Assignment 1-Marzan Wahab

** loading library**

```{r}
library(readr)
library(dplyr)
```
# Reading CSV file and Showing raw data
```{r}

Cereals <- read_csv("Cereals.csv")

View(Cereals) 
```
#outputs
```{r}

table(Cereals$mfr)

table(Cereals$type)

print("summary of sugars and fats")
summary(Cereals[,c("sugars","fat")])

Cereals %>%
  group_by(mfr) %>%
  summarise(
    count=n(),
    sugars=mean(sugars,na.rm=TRUE),
    fat=mean(fat,na.rm=TRUE),
    calories=mean(calories,na.rm=TRUE)
     )

Cereals %>%
  group_by(mfr) %>%
  summarise(
    count=n(),
    sugars=median (sugars,na.rm=TRUE),
    fat=median(fat,na.rm=TRUE),
    calories=median(calories,na.rm=TRUE)
     )

Cereals<-transform(Cereals,
                   calories_level=ifelse(calories>=90, "High","Low"))
print(Cereals)

plot(Cereals$calories,Cereals$sugars,
     main = "Sugar and Calories",
     xlab = "Calories",
     ylab = "Sugars",
     pch=20)
    
     